%-------------------------
% Resume in Latex
% Author : Solaiman Mansyur
% License : MIT
%------------------------

\documentclass[letterpaper,13pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formattin
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://solaiman.me/}{\Large Solaiman Mansyur}} & Email : \href{mailto:solaiman.mansyur@gmail.com}{solaiman.mansyur@gmail.com}\\
  \href{https://solaiman.me}{https://www.solaiman.me} & Mobile : +62-811-412-8485 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
    {AddEvent}{(Contractor via Yopeso)}
    {Backend Developer - Remote}{Mar 2022 - Present}
    \resumeItemListStart
      \resumeItem{Calendar \& Event Tools}
        {Migrating data layer \& API v2.0 development.}
      \resumeItem{iCal Generator}
        {Lead the development of iCal generator microservice.}
      \resumeItem{AB Testing Tool}
        {Lead the development of AB Testing Tool.}
    \resumeItemListEnd

    \resumeSubheading
      {Raffall}{(Contractor via Yopeso)}
      {PHP Web Developer - Remote}{Des 2020 - Feb 2022}
      \resumeItemListStart
        \resumeItem{Prize Competition Platform}
          {Stabilize, enhance, features development, and app \& infrastructure migration.}
      \resumeItemListEnd

    \resumeSubheading
      {Yopeso}{(Fulltime Contractor)}
      {PHP Web Developer - Remote}{Mar 2019 - Present}
      \resumeItemListStart
        \resumeItem{Venti \& GEP}
          {Global Supply and Demand platform for medical supplies around the globe, initiated during Covid-19 pandemic.}
        \resumeItem{Leave Management}
          {Web based multi-tenancy leave management.}
        \resumeItem{Bug Prediction \& Software Entropy}
          {Prediction with bug-caching methodology and software entropy calculation.}
    \resumeItemListEnd

    \resumeSubheading
      {Metacloud (Sunway Technology Group)}{(Permanent Employee)}
      {Senior Software Engineer - Onsite}{Jan 2017 - Feb 2019}
      \resumeItemListStart
        \resumeItem{3 Way Invoice Matching Integration}
          {ERPs, e-Procurement and Invoice Matching system integration.}
        \resumeItem{e-Procurement Platform}
          {From monolith to microservice architecture. Introduction to DevOps culture and CI/CD practices}
      \resumeItemListEnd

    \resumeSubheading
      {Logistics Consulting Asia}{(Fulltime Contractor)}
      {Application Developer - Onsite}{Sep 2015 - Jan 2017}
      \resumeItemListStart
        \resumeItem{Distributed data Syncrhonization}
          {Distributor Management System in more than 300 instances accross Asia.}
        \resumeItem{Data Warehouse and ETL}
          {Maintenance, operation and logging and monitoring of ETL process from OLTP into OLAP data.}
        \resumeItem{BI Dashboard}
          {Web-based Business Intelligence Dashboard.}
    \resumeItemListEnd

    \resumeSubheading
      {CloudApps Technologies}{(Independent Contractor)}
      {Senior Software Engineer - Remote}{Feb 2015 - Aug 2015}
      \resumeItemListStart
        \resumeItem{Cloud-Based Accounting Application}
          {SaaS accounting application on the cloud.}
      \resumeItemListEnd

    \resumeSubheading
      {ewakooLabs}{(Independent Contractor)}
      {Web Developer Freelancer - Onsite}{July 2012 - Jan 2015}
      \resumeItemListStart
        \resumeItem{Online University Submission}
          {A simulation of online submission of university. Used to simulate submission to a hundred of university in Indonesia.}
        \resumeItem{Taxi Cab Information System}
          {An Information system for a taxi cab.}
        \resumeItem{Point of Sales}
          {Point of Sales Application for the biggest Quran Publisher in Indonesia, Toha Putra.}
        \resumeItem{Government \& Private Projects}
          {Delivered several projects for Government institutions and companies in Indonesia.}
      \resumeItemListEnd

    \resumeSubheading
      {Jakarta Intensive Learning Center}{(Permanent Employee)}
      {Desktop Software Engineer \& Branch Manager - Onsite}{Sept 2007 - June 2012}
      \resumeItemListStart
        \resumeItem{Entire IT Needs}
          {From software development, networking, to working on a businesses level.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------Skills-----------------
\section{Skill Set}
  \resumeSubHeadingListStart
    \resumeSubItem{Fundamental Technical Concepts}
      {Software Architecture, Design Patterns, Agile, Technical Slicing, UML Diagram}
    \resumeSubItem{Software Development}
      {Fullstack Development, Containerization, DevOps \& CI CD, IaaC, Microservices, Test-driven Development}
    \resumeSubItem{Tech Stack}
      {Docker, MySQL, PostgreSQL, MongoDB, Redis, Memcached, PHP, Python, Golang, Javascript, AWS, K8s, Terraform}
    \resumeSubItem{Soft Skills}
      {Leadership, Mentoring, Teamwork, Communication, Problem Solving, Time Management, Self Management}
    \resumeSubItem{Language}
      {Bahasa Indonesia (Native), English (Professional), Arabic (Academic)}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Hasanuddin University}{Makassar, Indonesia}
      {Diploma in Electrical Engineering and Bachelor Degree in Information Technology}{Aug. 2004 -- Dec. 2012}
      \resumeItemListStart
        \resumeItem{Offline Mode CDMA Customer Registration}
          {CMDA Customer registration with offline mode support.}
        \resumeItem{Web Based CRM}
          {Research on how the CRM app can impact customer satisfcation for learning center businesses.}
      \resumeItemListEnd



  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
